%-------------------------
% Resume in Latex
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}


\usepackage{ifthen}


%%%%%%%%%%%%%%%  VARIABLES %%%%%%%%%%%%%%%
\newboolean{bigdata}
%\setboolean{bigdata}{true}
\setboolean{bigdata}{false}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\newcommand{\resumeSubHeadingEnvironmentAndTools}[1]{\textbf{Environment/Tools:}{ #1}}


\newcommand{\cplusplus}{C\texttt{++}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING-----------------

\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\Large Vasavi Aytha}} & Email : \href{mailto:vasavipravallika@gmail.com}{vasavipravallika@gmail.com}\\
  & Mobile : +1-209-782-7284 \\
\end{tabular*}


\begin{comment}
Engineering %age as far as I remeber is 86% (Or is it 76%?). Figure it out when you find time!!
\end{comment}

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {G Pulla Reddy College of Engineering and Technology}{Kurnool, India}
      {Bachelor of Engineering in Electrical and Electronics}{Aug. 2007 -- July. 2011}
  \resumeSubHeadingListEnd


%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
  \resumeSubHeadingListStart

    \resumeSubItem{Languages} {VBScript}
    \resumeSubItem{Databases} {DBSQL, MS SQL Server}
    \resumeSubItem{MS Office Tools} {MS-Word, MS-Excel MS-Outlook}
    \resumeSubItem{Testing Tools} {Quality Center, QTP, ALM}
    \resumeSubItem{Operating Systems} {Windows, Linux(Ubuntu)}
    
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      %https://www.deere.com/en/technology-products/precision-ag-technology/guidance/gen-4-premium-activation/
      {Kexim Bank}{Bangalore, India}
      {Quality Analyst}{Jun 2013 - Jul 2014}
      \resumeItemListStart
        \resumeItem{Gen4 CommandCenter\texttrademark\ Displays}
          {Develop software for displays of family of Autotrack guidance agriculture machines (like tractors) which farmers use for Presicion Agriculture.}
        \resumeItem{Defects Triaging}
          {Initial triaging/analysing of defects that are logged by farm testers to be assigned to right team. This needs a robust knowledge of the entire system and involves a lot of communication with various teams.}
        \resumeItem{Reprogramming Firmware}
          {Develop Reprogramming module which deals with installation and updates of Gen4 CommandCenter\texttrademark\ Display.}


        \ifthenelse {\boolean{bigdata}} { 
        \resumeItem{Statistical Analysis} 
          {Designed experiments and developed statistical analysis for global weather, crop and nutrients to quantify and predict related risks using scala.} 
        }
        {}


      \resumeItemListEnd
      \resumeSubHeadingEnvironmentAndTools{\cplusplus, Qt/QtCreatorIDE, python, \ifthenelse {\boolean{bigdata}} {Scala,} {}   bash, Multithreading, Agile, mercurial, git, CAN-protocol, sqlite-db, TestDrivenDevelopment(TDD), gtest, Squish(UI-Testing), Cucumber, gperf, valgrind, yum(package manager)}

    \resumeSubheading
      {Bloomberg}{Manhattan, NY}
      {Software Engineer}{Apr 2013 - May 2015}
      \resumeItemListStart
        \resumeItem{STEP (Add on software for OrderManagementSystem)}
         {Develop STEP Software which integrates with the various OMS products available in the market that helps traders to automate from sending IOIs (Indication of interest) and ADVs(Advertisement) without human intervention.}
        \resumeItem{Tool to test STEP}
         {Developed a test tool which will inject Orders that otherwise would have been sent by the associated OMS. This tool would generate all possible fix messages(like NewOrder/ FilledOrder/ PartialFill/ Cancel/ Replace) which was extensively used to test the main product (STEP) which we were developing.}
      \resumeItemListEnd
      \resumeSubHeadingEnvironmentAndTools{\cplusplus, JavaScript, Unix(AIX,  HP-UX,  Solaris), RAPID(UI development framework), SQL, ComDB, STL, FIX-protocol, Service orientied architecture, XML, Multithreading (IPC), OOP, svn.}


    \resumeSubheading
      %https://www.toshibatec.com/cnt/products_overseas/MFP/
      {Toshiba}{Bangalore, India}
      {Quality Analyst}{Aug 2011 - Feb 2013}
      \resumeItemListStart
        \resumeItem{Regression Testing}
          {Develop firmware for Toshiba's vast range of Multi Function Peripherals(MFPs) in \cplusplus and WindriverLinux.}
        \resumeItem{Onsite Coordinator}
          {Get involved with architecture team at client location and communicate the requirements to offshore team. Was in this role for about an year.}
        \resumeItem{Integration}
          {Integration of all three layers at the client location (Toshiba, Japan) by coordinating with all the teams.}
        \resumeItem{MFPUtility Libraries}
          {Develop algorithms/libraries specific to printers (like Magnification\%, Drawer selection, ExitTray selection, Staple/Duplex judgment.}
      \resumeItemListEnd
      \resumeSubHeadingEnvironmentAndTools{\cplusplus, Linux  IPCs,  Multithreading, Windriver  Linux,  PowerPC,  bash  scripting,  PVCS(version control), sqlite-db, awk, sed, valgrind}

    \resumeSubheading
      {Mindtree}{Bangalore, India}
      {Internship Project}{Dec 2005 - Mar 2006}
      \resumeItemListStart
\begin{comment}
Developing matlab model CVSD encoder/decoder for Bluetooth: 
\end{comment}
        \resumeItem{CVSD encode/decoder}
          {Develop a MATLAB model for CVSD encoder/decoder (which is an Audio CODEC) as per Bluetooth CVSD specification and do the performance analysis to find the best parameters.}
      \resumeItemListEnd
      %\resumeSubHeadingEnvironmentAndTools{Matlab, Bluetooth CVSD spec/algorithms, CVS}


  \resumeSubHeadingListEnd





\begin{comment}
%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{QuantSoftware Toolkit}
      {Open source python library for financial data analysis and machine learning for finance.}
    \resumeSubItem{Github Visualization}
      {Data Visualization of Git Log data using D3 to analyze project trends over time.}
    \resumeSubItem{Recommendation System}
      {Music and Movie recommender systems using collaborative filtering on public datasets.}
    \resumeSubItem{Mac Setup}
      {Book that gives step by step instructions on setting up developer environment on Mac OS.}
  \resumeSubHeadingListEnd
\end{comment}



%
%--------PROGRAMMING SKILLS------------
%\section{Programming Skills}
%  \resumeSubHeadingListStart
%    \item{
%      \textbf{Languages}{: Scala, Python, Javascript, \cplusplus, SQL, Java}
%      \hfill
%      \textbf{Technologies}{: AWS, Play, React, Kafka, GCE}
%    }
%  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
